---
title: "Analysis work flow"
author: "Xiaoyang Li"
date: "7/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
data = read.delim2("data_analysis.txt")
othmed_ = read.delim2("form501csum.txt")
```

_Foe the flow chart, I exclude the individual with no outcome_

### Use "F501 Q10 "Aside from the study drug, were any other anti-seizure medications administered within 60 min?

```{r}
table(data$antisewi60,data$med_use)
```

179 out of 477 used other anti-seizure medication within 60 minutes

```{r}
data1 = data %>% filter(antisewi60 == 1 & med_match ==1) 
sum(data1$med_matchA)
sum(data1$med_matchB)
sum(data1$med_matchC)
```

44 out of 179 received additional study medication as anti-seizure medication within 60 minutes, 21 of them received levetiracetam, 21 received fosphenytoin, and 2 of them received valproate.

```{r}
data2 = data1 %>% select(id, drug, outcome1, outcome2, med_match, med_matchA, med_matchB,med_matchC,med_use) %>% left_join(othmed_)

data3 = data2 %>% group_by(id) %>% summarise(summed = sum(omeduse))
```

