---
title: "Summary table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, warning = F,message = F)
```

```{r}
#library import
library(tidyverse)
library(readxl)

library(qwraps2)
options(qwraps2_markup = "markdown")

library(tidyverse)
library(ggplot2)
```


```{r Data clean}
Age = read_csv("E:/CU/RA/data/ESETT/Form 505.csv") %>% select(zSubjectID, age) %>% rename( id = zSubjectID)

Gender = read_csv("E:/CU/RA/data/ESETT/Form 127 gender.csv") %>% select(zSubjectID,agedist, Male)%>% rename( id = zSubjectID)

Pre = read_csv("E:/CU/RA/data/ESETT/CSV Datasets_form123.csv") %>% select(zSubjectID,F123Q06)%>% rename( id = zSubjectID, pre = F123Q06) %>%  
  mutate( pre = as.numeric(pre))

homemed = read_excel("E:/CU/RA/data/ESETT/Copy of Master_Results_Flattened.6.7.20.xlsx") %>% 
  janitor::clean_names() %>% 
  select(z_subject_id, home_meds_flat_med_name_1, home_meds_flat_med_name_2, home_meds_flat_med_name_3, home_meds_flat_med_name_4, home_meds_flat_med_name_5, home_meds_flat_med_name_6) %>% 
  rename(id = z_subject_id) %>% 
  pivot_longer(home_meds_flat_med_name_1:home_meds_flat_med_name_6, names_to = "med", values_to = "medname", names_prefix = "home_meds_flat_med_name_") %>% 
  mutate(medname = as.character(medname), id = as.numeric(id)) %>% 
  filter(medname != "NULL") 

homemed_num = homemed %>% 
  group_by(id) %>% 
  summarise(homemed_num = n())

# A = levetiracetam
# 
# B = Fosphenytoin
# 
# C = Valproate

homemed_match = homemed %>%
  mutate(matchA = case_when(medname == "Levetiracetam" ~ 1,
                            medname != "Levetiracetam" ~ 0),
         matchC = case_when(medname == "Valproate" ~ 1,
                            medname != "Valproate" ~ 0)) %>% 
  group_by(id) %>% summarise(sumA = sum(matchA), sumC = sum(matchC)) %>% 
  mutate(idmatchA = case_when(sumA > 0 ~ 1,
                              sumA == 0 ~ 0),
         idmatchC = case_when(sumC > 0 ~ 1,
                              sumC == 0 ~ 0)) 


homemed_s = homemed %>% 
  filter(medname != "Aspirin" & medname != "Naproxen" & medname != "Heparin"& medname != "Ibuprofen")#Aspirin Naproxen Heparin Ibuprofen 

length(unique(homemed_s$id)) #333

home_seizure_med = data.frame(id = unique(homemed_s$id), home_seizure_med = 1)


benzo = read_csv("E:/CU/RA/data/ESETT/Form 506MC.csv") %>% 
  janitor::clean_names() %>% 
  select(z_subject_id, f506cqb,f506cqa_min) %>% 
  rename(id = z_subject_id) %>% 
  mutate(f506cqa_min = as.numeric(f506cqa_min),
         time_before_drug = abs(f506cqa_min))

benzo$time_before_drug[is.na(benzo$time_before_drug)] = 0

benzo_dose = benzo %>% group_by(id) %>% summarise(dose_benzo = n(),
                                                  time_benzo = max(time_before_drug))


```

```{r}
data = read_excel("E:/CU/RA/data/ESETT/Copy of Master_Results_Flattened.6.7.20.xlsx") %>%
  janitor::clean_names() %>% 
  dplyr::select(z_subject_id, sz_at_60mins, responsive_at_60mins, outcome1a_treatment_success_adjudicated_1_yes_0_no,  children, se_duration_before_study_drug, benzos_pre_ed, study_drug, se_precipitnat, race, hispanic, itt, final_dx) %>% 
  rename(id = z_subject_id,
         sz60 = sz_at_60mins,
         res60 = responsive_at_60mins,
         outcome = outcome1a_treatment_success_adjudicated_1_yes_0_no,
         se = se_duration_before_study_drug,
         drug = study_drug,
         cause = se_precipitnat)

data = data %>%
  mutate(id = as.numeric(id),
         benzos_pre_ed = as.numeric(benzos_pre_ed), 
         sz60 = as.numeric(sz60),
         res60 = as.numeric(res60), 
         se = as.numeric(se),
         itt = as.numeric(itt)) 


data = data %>% 
  full_join(Age) %>% full_join(Gender) %>% full_join(Pre) %>% full_join(homemed_num) %>% full_join(homemed_match) %>% full_join(home_seizure_med) %>% full_join(benzo_dose) %>% 
  mutate(age_group = case_when(age < 18 ~ "child",
                     age >= 18 & age < 60 ~ "adult",
                     age >= 60 ~ "senior"), 
         se_group = case_when(se < 30 ~ "[0,30)",
                     se >= 30 & se < 60 ~ "[30,60)",
                     se >= 60 ~ "[60,)"), 
         success = case_when(sz60 == 0 & res60 == 1 ~ 1,
                            sz60 != 0 | res60 != 1 ~ 0),
         provoked = case_when(cause != "Unprovoked" ~ "Yes",
                              cause == "Unprovoked" ~ "No")) %>%
  dplyr::select( -agedist)

data = data %>% filter(!is.na(success) & itt == 1 & final_dx != "Non-epileptic spell") 

# ???
data$homemed_num[is.na(data$homemed_num)] = 0
data$homemed_num[is.na(data$idmatchA)] = 0
data$homemed_num[is.na(data$idmatchC)] = 0
data$home_seizure_med[is.na(data$home_seizure_med)] = 0
```


```{r}
Data = data  %>%
  dplyr::select(-hispanic, -race, -cause, -children) %>% 
  mutate(age_group = factor(age_group, levels = c("child", "adult", "senior" )),
         gender = recode(data$Male, "0" = "Female", "1" = "Male"),
         homemed = recode(data$home_seizure_med, "0" = "No", "1" = "Yes"),
         se_group = factor(se_group, levels = c("[0,30)", "[30,60)", "[60,)" )),
         benzo = recode(data$benzos_pre_ed, "0" = "No", "1" = "Yes"),
         benzonum = case_when(dose_benzo <= 2 ~ "1~2",
                              dose_benzo > 2 ~ "3~7"),
         time =  case_when(time_benzo < 15 ~ "[0,15)",
                     time_benzo >= 15 & time_benzo < 30 ~ "[15,30)",
                     time_benzo >= 30 & time_benzo < 45 ~ "[30,45)",
                     time_benzo >= 45 ~ "[45,)")) 


write.csv(Data,file = "./data/newData.csv")

```

## Sample size

478 events in the original dataset, one of them is excluded due to lack of outcome (outcome = NA). -> n = 477

After removing 16 repeat visits (itt = 0), there are 461 patients in total, -> n = 461

There are 421 patients after removing 40 non-epileptic (final_dx = "Non-epileptic spell") -> n = 421

## Tables 1 include 421 patients by treatment

```{r}

sum <- list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd( age),
      "Range" = ~ paste(min( age),max( age), sep = "-"),
      "NA" = ~ paste0(sum(is.na( age)),"(",round(sum(is.na( age)) / length( id) *100,2), "%)")
    ),
  "Age Group" = 
    list(
      "0-17y" = ~ qwraps2::n_perc( age<= 17),
      "18y - 60 y" = ~ qwraps2::n_perc( age >= 18 &  age <= 60),
      ">60 y" = ~ qwraps2::n_perc( age>60)
    ),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc( Male == 0),
      "Male" = ~ qwraps2::n_perc( Male == 1)),
  "Race" = 
    list(
      "Black" = ~ qwraps2::n_perc( race == "Black/African American"),
      "White" = ~ qwraps2::n_perc( race == "White"),
      "Asian" = ~ qwraps2::n_perc( race == "Asian"),
      "Other" = ~ qwraps2::n_perc( race != "White" &  race != "Black/African American" &  race != "Asian" &  race != "Unknown" ),
      "Unknown" = ~ qwraps2::n_perc( race == "Unknown")
    ),
  "Ethnicity" = 
    list(
      "Hispanic" = ~ qwraps2::n_perc( hispanic == "1"),
      "Non-Hispanic" = ~ qwraps2::n_perc( hispanic == "0")
    ),
  "Home antiepileptic medications" = 
    list(
      "0" = ~  qwraps2::n_perc( homemed_num == "0"),
      "1" = ~  qwraps2::n_perc( homemed_num == "1"),
      "2" = ~  qwraps2::n_perc( homemed_num == "2"),
      "3" = ~  qwraps2::n_perc( homemed_num == "3"),
      "4" = ~  qwraps2::n_perc( homemed_num == "4"),
      "5" = ~  qwraps2::n_perc( homemed_num == "5"),
      "6" = ~  qwraps2::n_perc( homemed_num == "6")
    ),
  "History of epilepsy" = 
    list(
      "Yes" = ~ qwraps2::n_perc( pre[!is.na( pre)] == 1),
      "No" = ~  qwraps2::n_perc( pre[!is.na( pre)] == 0),
      "NA" = ~ paste0(sum(is.na( pre)),"(",round(sum(is.na( pre)) / length( id) *100,2), "%)")
    ),
  "Duration of seizure" = list(
    "mean (sd)" = ~  mean_sd( se[!is.na( se)]),
    "Range" = ~ paste(min( se[!is.na( se)]),max( se[!is.na( se)]), sep = "-"),
    "NA" = ~ paste0(sum(is.na( se)),"(",round(sum(is.na( se)) / length( id) *100,2), "%)")
  ),
  "Benzodiazepines given before ED arrival" = list(
    
    "Yes" = ~ qwraps2::n_perc( benzos_pre_ed[!is.na( benzos_pre_ed)] == 1),
    "No" = ~  qwraps2::n_perc( benzos_pre_ed[!is.na( benzos_pre_ed)] == 0),
    "NA" = ~ paste0(sum(is.na( benzos_pre_ed)),"(",round(sum(is.na( benzos_pre_ed)) / length( id) *100,2), "%)")
  ),
  "Number of benzo doses" = list(
    "mean (sd)" = ~  mean_sd( dose_benzo),
    "Range" = ~ paste(min( dose_benzo),max( dose_benzo), sep = "-"),
    "NA" = ~ paste0(sum(is.na( dose_benzo)),"(",round(sum(is.na( dose_benzo)) / length( id) *100,2), "%)"),
    
    "0" = ~  qwraps2::n_perc( dose_benzo == "0"),
    "1" = ~  qwraps2::n_perc( dose_benzo == "1"),
    "2" = ~  qwraps2::n_perc( dose_benzo == "2"),
    "3" = ~  qwraps2::n_perc( dose_benzo == "3"),
    "4" = ~  qwraps2::n_perc( dose_benzo == "4"),
    "5" = ~  qwraps2::n_perc( dose_benzo == "5"),
    "6" = ~  qwraps2::n_perc( dose_benzo == "6"),
    "7" = ~  qwraps2::n_perc( dose_benzo == "7")
  ),
  "Interval between 1st dose of benzo and administration of the study drug" = list(
    "mean (sd)" = ~  mean_sd( time_benzo),
    "Range" = ~ paste(min( time_benzo),max( time_benzo), sep = "-"),
    "NA" = ~ paste0(sum(is.na( time_benzo)),"(",round(sum(is.na( time_benzo)) / length( id) *100,2), "%)")
    
  )
)

drug_sep = summary_table(group_by(data, drug), sum)
whole = summary_table(data, sum)

cbind(whole, drug_sep)

```


|                                                                            |data (N = 421)       |A (N = 159)          |B (N = 131)          |C (N = 131)          |
|:---------------------------------------------------------------------------|:--------------------|:--------------------|:--------------------|:--------------------|
|**Age**                                                                     |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                      |28.19 &plusmn; 26.22 |28.80 &plusmn; 26.86 |27.28 &plusmn; 25.45 |28.35 &plusmn; 26.38 |
|&nbsp;&nbsp; Range                                                          |1-94                 |1-94                 |1-84                 |1-85                 |
|&nbsp;&nbsp; NA                                                             |0(0%)                |0(0%)                |0(0%)                |0(0%)                |
|**Age Group**                                                               |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; 0-17y                                                          |217 (51.54%)         |81 (50.94%)          |70 (53.44%)          |66 (50.38%)          |
|&nbsp;&nbsp; 18y - 60 y                                                     |135 (32.07%)         |54 (33.96%)          |39 (29.77%)          |42 (32.06%)          |
|&nbsp;&nbsp; >60 y                                                          |69 (16.39%)          |24 (15.09%)          |22 (16.79%)          |23 (17.56%)          |
|**Gender**                                                                  |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Female                                                         |176 (41.81%)         |69 (43.40%)          |52 (39.69%)          |55 (41.98%)          |
|&nbsp;&nbsp; Male                                                           |245 (58.19%)         |90 (56.60%)          |79 (60.31%)          |76 (58.02%)          |
|**Race**                                                                    |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Black                                                          |182 (43.23%)         |70 (44.03%)          |51 (38.93%)          |61 (46.56%)          |
|&nbsp;&nbsp; White                                                          |179 (42.52%)         |68 (42.77%)          |59 (45.04%)          |52 (39.69%)          |
|&nbsp;&nbsp; Asian                                                          |17 (4.04%)           |7 (4.40%)            |5 (3.82%)            |5 (3.82%)            |
|&nbsp;&nbsp; Other                                                          |11 (2.61%)           |5 (3.14%)            |3 (2.29%)            |3 (2.29%)            |
|&nbsp;&nbsp; Unknown                                                        |32 (7.60%)           |9 (5.66%)            |13 (9.92%)           |10 (7.63%)           |
|**Ethnicity**                                                               |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Hispanic                                                       |71 (16.86%)          |28 (17.61%)          |19 (14.50%)          |24 (18.32%)          |
|&nbsp;&nbsp; Non-Hispanic                                                   |350 (83.14%)         |131 (82.39%)         |112 (85.50%)         |107 (81.68%)         |
|**Home antiepileptic medications**                                          |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; 0                                                              |107 (25.42%)         |40 (25.16%)          |29 (22.14%)          |38 (29.01%)          |
|&nbsp;&nbsp; 1                                                              |125 (29.69%)         |47 (29.56%)          |42 (32.06%)          |36 (27.48%)          |
|&nbsp;&nbsp; 2                                                              |97 (23.04%)          |37 (23.27%)          |34 (25.95%)          |26 (19.85%)          |
|&nbsp;&nbsp; 3                                                              |48 (11.40%)          |17 (10.69%)          |17 (12.98%)          |14 (10.69%)          |
|&nbsp;&nbsp; 4                                                              |24 (5.70%)           |9 (5.66%)            |4 (3.05%)            |11 (8.40%)           |
|&nbsp;&nbsp; 5                                                              |14 (3.33%)           |6 (3.77%)            |4 (3.05%)            |4 (3.05%)            |
|&nbsp;&nbsp; 6                                                              |6 (1.43%)            |3 (1.89%)            |1 (0.76%)            |2 (1.53%)            |
|**History of epilepsy**                                                     |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Yes                                                            |305 (72.79%)         |112 (70.89%)         |98 (75.38%)          |95 (72.52%)          |
|&nbsp;&nbsp; No                                                             |114 (27.21%)         |46 (29.11%)          |32 (24.62%)          |36 (27.48%)          |
|&nbsp;&nbsp; NA                                                             |2(0.48%)             |1(0.63%)             |1(0.76%)             |0(0%)                |
|**Duration of seizure**                                                     |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                      |77.47 &plusmn; 60.07 |73.72 &plusmn; 46.88 |80.96 &plusmn; 72.33 |78.57 &plusmn; 61.25 |
|&nbsp;&nbsp; Range                                                          |6-620                |6-305                |10-620               |10-377               |
|&nbsp;&nbsp; NA                                                             |29(6.89%)            |10(6.29%)            |10(7.63%)            |9(6.87%)             |
|**Benzodiazepines given before ED arrival**                                 |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Yes                                                            |192 (55.49%)         |78 (59.54%)          |61 (57.01%)          |53 (49.07%)          |
|&nbsp;&nbsp; No                                                             |154 (44.51%)         |53 (40.46%)          |46 (42.99%)          |55 (50.93%)          |
|&nbsp;&nbsp; NA                                                             |75(17.81%)           |28(17.61%)           |24(18.32%)           |23(17.56%)           |
|**Number of benzo doses**                                                   |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                      |2.48 &plusmn; 0.94   |2.56 &plusmn; 0.97   |2.47 &plusmn; 0.89   |2.39 &plusmn; 0.97   |
|&nbsp;&nbsp; Range                                                          |1-7                  |1-7                  |1-5                  |1-6                  |
|&nbsp;&nbsp; NA                                                             |0(0%)                |0(0%)                |0(0%)                |0(0%)                |
|&nbsp;&nbsp; 0                                                              |0 (0.00%)            |0 (0.00%)            |0 (0.00%)            |0 (0.00%)            |
|&nbsp;&nbsp; 1                                                              |49 (11.64%)          |16 (10.06%)          |14 (10.69%)          |19 (14.50%)          |
|&nbsp;&nbsp; 2                                                              |188 (44.66%)         |65 (40.88%)          |60 (45.80%)          |63 (48.09%)          |
|&nbsp;&nbsp; 3                                                              |130 (30.88%)         |58 (36.48%)          |40 (30.53%)          |32 (24.43%)          |
|&nbsp;&nbsp; 4                                                              |45 (10.69%)          |16 (10.06%)          |15 (11.45%)          |14 (10.69%)          |
|&nbsp;&nbsp; 5                                                              |6 (1.43%)            |2 (1.26%)            |2 (1.53%)            |2 (1.53%)            |
|&nbsp;&nbsp; 6                                                              |2 (0.48%)            |1 (0.63%)            |0 (0.00%)            |1 (0.76%)            |
|&nbsp;&nbsp; 7                                                              |1 (0.24%)            |1 (0.63%)            |0 (0.00%)            |0 (0.00%)            |
|**Interval between 1st dose of benzo and administration of the study drug** |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                      |49.59 &plusmn; 63.11 |49.99 &plusmn; 45.72 |51.98 &plusmn; 80.04 |46.70 &plusmn; 62.51 |
|&nbsp;&nbsp; Range                                                          |5-857                |6-335                |7-857                |5-557                |
|&nbsp;&nbsp; NA                                                             |0(0%)                |0(0%)                |0(0%)                |0(0%)                |

## Table 2 Seizure types

```{r}
type = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(data$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(data$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(data$cause == "CNS infection" | data$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(data$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(data$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(data$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(data$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(data$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(data$cause == "Other")
    )
)

Success.A = A %>% filter(success == 1)
Success.B = B %>% filter(success == 1)
Success.C = C %>% filter(success == 1)

Failure.A = A %>% filter(success == 0)
Failure.B = B %>% filter(success == 0)
Failure.C = C %>% filter(success == 0)

typesa = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Success.A$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Success.A$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Success.A$cause == "CNS infection" | Success.A$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Success.A$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Success.A$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Success.A$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Success.A$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Success.A$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Success.A$cause == "Other")
    )
)

typesb = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Success.B$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Success.B$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Success.B$cause == "CNS infection" | Success.B$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Success.B$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Success.B$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Success.B$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Success.B$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Success.B$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Success.B$cause == "Other")
    )
)

typesc = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Success.C$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Success.C$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Success.C$cause == "CNS infection" | Success.C$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Success.C$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Success.C$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Success.C$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Success.C$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Success.C$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Success.C$cause == "Other")
    )
)

typefa = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Failure.A$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Failure.A$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Failure.A$cause == "CNS infection" | Failure.A$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Failure.A$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Failure.A$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Failure.A$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Failure.A$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Failure.A$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Failure.A$cause == "Other")
    )
)

typefb = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Failure.B$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Failure.B$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Failure.B$cause == "CNS infection" | Failure.B$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Failure.B$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Failure.B$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Failure.B$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Failure.B$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Failure.B$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Failure.B$cause == "Other")
    )
)

typefc = list(
  "Seizure Type" = 
    list(
      "Stroke"= ~ qwraps2::n_perc(Failure.C$cause == "Acute stroke/Hemorrhage"),
      "Electrolyte anomalies"= ~ qwraps2::n_perc(Failure.C$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "CNS Tumors/CNS infection"= ~ qwraps2::n_perc(Failure.C$cause == "CNS infection" | Failure.C$cause == "CNS tumor\r"),
      "Unprovoked"= ~ qwraps2::n_perc(Failure.C$cause == "Unprovoked"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(Failure.C$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "Febrile illness"= ~ qwraps2::n_perc(Failure.C$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(Failure.C$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(Failure.C$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Other"= ~ qwraps2::n_perc(Failure.C$cause == "Other")
    )
)

saT = summary_table(Success.A,typesa)
sbT = summary_table(Success.B,typesb)
scT = summary_table(Success.C,typesc)
faT = summary_table(Failure.A,typefa)
fbT = summary_table(Failure.B,typefb)
fcT = summary_table(Failure.C,typefc)

cbind(saT,sbT,scT,faT,fbT,fcT)

```
|                                                                          |Success.A (N = 93) |Success.B (N = 71) |Success.C (N = 77) |Failure.A (N = 66) |Failure.B (N = 60) |Failure.C (N = 54) |
|:-------------------------------------------------------------------------|:------------------|:------------------|:------------------|:------------------|:------------------|:------------------|
|**Seizure Type**                                                          |&nbsp;&nbsp;       |&nbsp;&nbsp;       |&nbsp;&nbsp;       |&nbsp;&nbsp;       |&nbsp;&nbsp;       |&nbsp;&nbsp;       |
|&nbsp;&nbsp; Stroke                                                       |3 (3.23%)          |4 (5.63%)          |1 (1.30%)          |3 (4.55%)          |4 (6.67%)          |2 (3.70%)          |
|&nbsp;&nbsp; Electrolyte anomalies                                        |2 (2.15%)          |0 (0.00%)          |0 (0.00%)          |1 (1.52%)          |2 (3.33%)          |1 (1.85%)          |
|&nbsp;&nbsp; CNS Tumors/CNS infection                                     |1 (1.08%)          |3 (4.23%)          |0 (0.00%)          |4 (6.06%)          |2 (3.33%)          |5 (9.26%)          |
|&nbsp;&nbsp; Unprovoked                                                   |32 (34.41%)        |22 (30.99%)        |27 (35.06%)        |23 (34.85%)        |28 (46.67%)        |12 (22.22%)        |
|&nbsp;&nbsp; Anti-epileptic drug withdrawal/non compliance                |14 (15.05%)        |10 (14.08%)        |13 (16.88%)        |10 (15.15%)        |5 (8.33%)          |3 (5.56%)          |
|&nbsp;&nbsp; Febrile illness                                              |22 (23.66%)        |16 (22.54%)        |20 (25.97%)        |9 (13.64%)         |8 (13.33%)         |15 (27.78%)        |
|&nbsp;&nbsp; Insufficient information to determine/idiopathic/cryptogenic |0 (0.00%)          |2 (2.82%)          |4 (5.19%)          |7 (10.61%)         |1 (1.67%)          |4 (7.41%)          |
|&nbsp;&nbsp; Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)  |6 (6.45%)          |3 (4.23%)          |3 (3.90%)          |5 (7.58%)          |3 (5.00%)          |5 (9.26%)          |
|&nbsp;&nbsp; Other                                                        |13 (13.98%)        |11 (15.49%)        |9 (11.69%)         |4 (6.06%)          |7 (11.67%)         |7 (12.96%)         |



