---
title: "Cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F,message = F)
```

```{r}
#library import
library(tidyverse)
library(readxl)

library(qwraps2)
options(qwraps2_markup = "markdown")
```

## Data clean


```{r}
Age = read_csv("C:/Users/Xiaoyang Li/Desktop/data/ESETT/Form 505.csv") %>% select(zSubjectID, age) %>% rename( id = zSubjectID)

Gender = read_csv("C:/Users/Xiaoyang Li/Desktop/data/ESETT/Form 127 gender.csv") %>% select(zSubjectID,agedist, Male)%>% rename( id = zSubjectID)

Pre = read_csv("C:/Users/Xiaoyang Li/Desktop/data/ESETT/CSV Datasets_form123.csv") %>% select(zSubjectID,F123Q06)%>% rename( id = zSubjectID, pre = F123Q06) %>%  
  mutate( pre = as.numeric(pre))
        

data = read_excel("C:/Users/Xiaoyang Li/Desktop/data/ESETT/Copy of Master_Results_Flattened.6.7.20.xlsx") %>% 
  janitor::clean_names() %>% 
  select(z_subject_id, race, children, outcome1a_treatment_success_adjudicated_1_yes_0_no, lor_equiv_lt_32kg, lor_equic_gt_32kg,weightkg, study_drug, se_precipitnat)%>% 
  rename(id = z_subject_id,
        outcome = outcome1a_treatment_success_adjudicated_1_yes_0_no,
        lorlt = lor_equiv_lt_32kg,
        lorgt = lor_equic_gt_32kg,
        drug = study_drug,
        cause = se_precipitnat) %>% 
  mutate(id = as.numeric(id),
         lorlt = as.numeric(lorlt),
         lorgt = as.numeric(lorgt),
         weightkg = as.numeric(weightkg),
         outcome = as.numeric(outcome)
         )
str(data$outcome)
sum(is.na(data$outcome))
data = full_join(data, Age)
data = full_join(data,Gender)
data = full_join(data, Pre)
```


## Summary Table
```{r}
drugA = data %>% filter(drug == "A")
drugB = data %>% filter(drug == "B")
drugC = data %>% filter(drug == "C")

sum = list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd(data$age),
      "Range" = ~ paste(min(data$age),max(data$age), sep = "-")),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc(data$Male == 0),
      "Male" = ~ qwraps2::n_perc(data$Male == 1)),
  "Race" = 
    list(
      "Black" = ~ qwraps2::n_perc(data$race == "Black/African American"),
      "White" = ~ qwraps2::n_perc(data$race == "White"),
      "Asian" = ~ qwraps2::n_perc(data$race == "Asian"),
      "Other" = ~ qwraps2::n_perc(data$race != "White" & data$race != "Black/African American" & data$race != "Asian" & data$race != "Unknown" ),
      "Unknown" = ~ qwraps2::n_perc(data$race == "Unknown")
    ),
  "Ethnicity" = 
    list(
      "Hispanic" = ~ qwraps2::n_perc(data$hispanic == "1"),
      "Non-Hispanic" = ~ qwraps2::n_perc(data$hispanic == "0")
    ),
  "Weight(Kg)" = 
    list(
      "mean (sd)" = ~  mean_sd(data$weightkg),
      "Range" = ~ paste(min(data$weightkg),max(data$weightkg), sep = "-")),
  "History of epilepsy" = 
    list(
      "Yes" = ~ qwraps2::n_perc(data$pre[!is.na(data$pre)] == 1),
      "No" = ~  qwraps2::n_perc(data$pre[!is.na(data$pre)] == 0),
      "NA" = ~ paste0(sum(is.na(data$pre)),"(",round(sum(is.na(data$pre)) / 478 *100,2), "%)")
    ),
  "Aetiology" = 
    list(
      "Acute stroke/Hemorrhage"= ~ qwraps2::n_perc(data$cause == "Acute stroke/Hemorrhage"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(data$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "CNS infection"= ~ qwraps2::n_perc(data$cause == "CNS infection"),
      "CNS tumor"= ~ qwraps2::n_perc(data$cause == "CNS tumor\r"),
      "Febrile illness"= ~ qwraps2::n_perc(data$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(data$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Metabolic (hypoglycemia, hyponatremia, etc.)"= ~ qwraps2::n_perc(data$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(data$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Unprovoked"= ~ qwraps2::n_perc(data$cause == "Unprovoked"),
      "Other"= ~ qwraps2::n_perc(data$cause == "Other")
  ),
  "Lorazepam equivalents" = 
    list(
      "In mg for those weighing ≥32 kg" = ~  mean_sd(data$lorgt[!is.na(data$lorgt)]),
      "NA" = ~ paste0(sum(is.na(data$lorgt)),"(",round(sum(is.na(data$pre)) / 478 *100,2), "%)"),
      "In mg/kg for those weighing <32 kg" = ~  mean_sd(data$lorlt[!is.na(data$lorlt)]),
      "NA" = ~ paste0(sum(is.na(data$lorlt)),"(",round(sum(is.na(data$pre)) / 478 *100,2), "%)")),
  "Success" =
    list(
      percentage = ~ qwraps2::n_perc(data$outcome == 1)
    )
)

data$cause

drugAG = drugA %>% filter(weightkg>=32)
drugAL = drugA %>% filter(weightkg<32)
  
sumA = list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd(drugA$age),
      "Range" = ~ paste(min(drugA$age),max(drugA$age), sep = "-")),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc(drugA$Male == 0),
      "Male" = ~ qwraps2::n_perc(drugA$Male == 1)),
  "Race" = 
    list(
      "Black" = ~ qwraps2::n_perc(drugA$race == "Black/African American"),
      "White" = ~ qwraps2::n_perc(drugA$race == "White"),
      "Asian" = ~ qwraps2::n_perc(drugA$race == "Asian"),
      "Other" = ~ qwraps2::n_perc(drugA$race != "White" & drugA$race != "Black/African American" & drugA$race != "Asian" & drugA$race != "Unknown" ),
      "Unknown" = ~ qwraps2::n_perc(drugA$race == "Unknown")
    ),
  "Ethnicity" = 
    list(
      "Hispanic" = ~ qwraps2::n_perc(drugA$hispanic == "1"),
      "Non-Hispanic" = ~ qwraps2::n_perc(drugA$hispanic == "0")
    ),
  "Weight(Kg)" = 
    list(
      "mean (sd)" = ~  mean_sd(drugA$weightkg),
      "Range" = ~ paste(min(drugA$weightkg),max(drugA$weightkg), sep = "-")),
  "History of epilepsy" = 
    list(
      "Yes" = ~ qwraps2::n_perc(drugA$pre[!is.na(drugA$pre)] == 1),
      "No" = ~  qwraps2::n_perc(drugA$pre[!is.na(drugA$pre)] == 0),
      "NA" = ~ paste0(sum(is.na(drugA$pre)),"(",round(sum(is.na(drugA$pre)) / 180 *100,2), "%)")
    ),
  "Aetiology" = 
    list(
      "Acute stroke/Hemorrhage"= ~ qwraps2::n_perc(drugA$cause == "Acute stroke/Hemorrhage"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(drugA$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "CNS infection"= ~ qwraps2::n_perc(drugA$cause == "CNS infection"),
      "CNS tumor"= ~ qwraps2::n_perc(drugA$cause == "CNS tumor\r"),
      "Febrile illness"= ~ qwraps2::n_perc(drugA$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(drugA$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Metabolic (hypoglycemia, hyponatremia, etc.)"= ~ qwraps2::n_perc(drugA$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(drugA$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Unprovoked"= ~ qwraps2::n_perc(drugA$cause == "Unprovoked"),
      "Other"= ~ qwraps2::n_perc(drugA$cause == "Other")
    ),
  "Lorazepam equivalents" = 
    list(
      "In mg for those weighing ≥32 kg" = ~  mean_sd(drugAG$lorgt[!is.na(drugAG$lorgt)]),
      "NA" = ~ paste0(sum(is.na(drugAG$lorgt)),"(",round(sum(is.na(drugAG$pre)) / 112 *100,2), "%)"),
      "In mg/kg for those weighing <32 kg" = ~  mean_sd(drugAL$lorlt[!is.na(drugAL$lorlt)]),
      "NA" = ~ paste0(sum(is.na(drugAL$lorlt)),"(",round(sum(is.na(drugAL$pre)) / 68 *100,2), "%)")),
  "Success" =
    list(
      percentage = ~ qwraps2::n_perc(drugA$outcome == 1)
    )
)


drugBG = drugB %>% filter(weightkg>=32)
drugBL = drugB %>% filter(weightkg<32)

sumB = list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd(drugB$age),
      "Range" = ~ paste(min(drugB$age),max(drugB$age), sep = "-")),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc(drugB$Male == 0),
      "Male" = ~ qwraps2::n_perc(drugB$Male == 1)),
  "Race" = 
    list(
      "Black" = ~ qwraps2::n_perc(drugB$race == "Black/African American"),
      "White" = ~ qwraps2::n_perc(drugB$race == "White"),
      "Asian" = ~ qwraps2::n_perc(drugB$race == "Asian"),
      "Other" = ~ qwraps2::n_perc(drugB$race != "White" & drugB$race != "Black/African American" & drugB$race != "Asian" & drugB$race != "Unknown" ),
      "Unknown" = ~ qwraps2::n_perc(drugB$race == "Unknown")
    ),
  "Ethnicity" = 
    list(
      "Hispanic" = ~ qwraps2::n_perc(drugB$hispanic == "1"),
      "Non-Hispanic" = ~ qwraps2::n_perc(drugB$hispanic == "0")
    ),
  "Weight(Kg)" = 
    list(
      "mean (sd)" = ~  mean_sd(drugB$weightkg),
      "Range" = ~ paste(min(drugB$weightkg),max(drugB$weightkg), sep = "-")),
  "History of epilepsy" = 
    list(
      "Yes" = ~ qwraps2::n_perc(drugB$pre[!is.na(drugB$pre)] == 1),
      "No" = ~  qwraps2::n_perc(drugB$pre[!is.na(drugB$pre)] == 0),
      "NA" = ~ paste0(sum(is.na(drugB$pre)),"(",round(sum(is.na(drugB$pre)) / 149 *100,2), "%)")
    ),
  "Aetiology" = 
    list(
      "Acute stroke/Hemorrhage"= ~ qwraps2::n_perc(drugB$cause == "Acute stroke/Hemorrhage"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(drugB$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "CNS infection"= ~ qwraps2::n_perc(drugB$cause == "CNS infection"),
      "CNS tumor"= ~ qwraps2::n_perc(drugB$cause == "CNS tumor\r"),
      "Febrile illness"= ~ qwraps2::n_perc(drugB$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(drugB$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Metabolic (hypoglycemia, hyponatremia, etc.)"= ~ qwraps2::n_perc(drugB$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(drugB$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Unprovoked"= ~ qwraps2::n_perc(drugB$cause == "Unprovoked"),
      "Other"= ~ qwraps2::n_perc(drugB$cause == "Other")
    ),
  "Lorazepam equivalents" = 
    list(
      "In mg for those weighing ≥32 kg" = ~  mean_sd(drugBG$lorgt[!is.na(drugBG$lorgt)]),
      "NA" = ~ paste0(sum(is.na(drugBG$lorgt)),"(",round(sum(is.na(drugBG$pre)) / 86 *100,2), "%)"),
      "In mg/kg for those weighing <32 kg" = ~  mean_sd(drugBL$lorlt[!is.na(drugBL$lorlt)]),
      "NA" = ~ paste0(sum(is.na(drugBL$lorlt)),"(",round(sum(is.na(drugBL$pre)) / 63 *100,2), "%)")),
  "Success" =
    list(
      percentage = ~ qwraps2::n_perc(drugB$outcome == 1)
    )
)


drugCG = drugC %>% filter(weightkg>=32)
drugCL = drugC %>% filter(weightkg<32)

sumC = list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd(drugC$age),
      "Range" = ~ paste(min(drugC$age),max(drugC$age), sep = "-")),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc(drugC$Male == 0),
      "Male" = ~ qwraps2::n_perc(drugC$Male == 1)),
  "Race" = 
    list(
      "Black" = ~ qwraps2::n_perc(drugC$race == "Black/African American"),
      "White" = ~ qwraps2::n_perc(drugC$race == "White"),
      "Asian" = ~ qwraps2::n_perc(drugC$race == "Asian"),
      "Other" = ~ qwraps2::n_perc(drugC$race != "White" & drugC$race != "Black/African American" & drugC$race != "Asian" & drugC$race != "Unknown" ),
      "Unknown" = ~ qwraps2::n_perc(drugC$race == "Unknown")
    ),
  "Ethnicity" = 
    list(
      "Hispanic" = ~ qwraps2::n_perc(drugC$hispanic == "1"),
      "Non-Hispanic" = ~ qwraps2::n_perc(drugC$hispanic == "0")
    ),
  "Weight(Kg)" = 
    list(
      "mean (sd)" = ~  mean_sd(drugC$weightkg),
      "Range" = ~ paste(min(drugC$weightkg),max(drugC$weightkg), sep = "-")),
  "History of epilepsy" = 
    list(
      "Yes" = ~ qwraps2::n_perc(drugC$pre[!is.na(drugC$pre)] == 1),
      "No" = ~  qwraps2::n_perc(drugC$pre[!is.na(drugC$pre)] == 0),
      "NA" = ~ paste0(sum(is.na(drugC$pre)),"(",round(sum(is.na(drugC$pre)) / 149 *100,2), "%)")
    ),
  "Aetiology" = 
    list(
      "Acute stroke/Hemorrhage"= ~ qwraps2::n_perc(drugC$cause == "Acute stroke/Hemorrhage"),
      "Anti-epileptic drug withdrawal/non compliance"= ~ qwraps2::n_perc(drugC$cause == "Anti-epileptic drug withdrawal/non compliance"),
      "CNS infection"= ~ qwraps2::n_perc(drugC$cause == "CNS infection"),
      "CNS tumor"= ~ qwraps2::n_perc(drugC$cause == "CNS tumor\r"),
      "Febrile illness"= ~ qwraps2::n_perc(drugC$cause == "Febrile illness"),
      "Insufficient information to determine/idiopathic/cryptogenic"= ~ qwraps2::n_perc(drugC$cause == "Insufficient information to determine/idiopathic/cryptogenic"),
      "Metabolic (hypoglycemia, hyponatremia, etc.)"= ~ qwraps2::n_perc(drugC$cause == "Metabolic (hypoglycemia, hyponatremia, etc.)\r"),
      "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"= ~ qwraps2::n_perc(drugC$cause == "Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)"),
      "Unprovoked"= ~ qwraps2::n_perc(drugC$cause == "Unprovoked"),
      "Other"= ~ qwraps2::n_perc(drugC$cause == "Other")
    ),
  "Lorazepam equivalents" = 
    list(
      "In mg for those weighing ≥32 kg" = ~  mean_sd(drugCG$lorgt[!is.na(drugCG$lorgt)]),
      "NA" = ~ paste0(sum(is.na(drugCG$lorgt)),"(",round(sum(is.na(drugCG$pre)) / 95 *100,2), "%)"),
      "In mg/kg for those weighing <32 kg" = ~  mean_sd(drugCL$lorlt[!is.na(drugCL$lorlt)]),
      "NA" = ~ paste0(sum(is.na(drugCL$lorlt)),"(",round(sum(is.na(drugCL$pre)) / 54 *100,2), "%)")),
  "Success" =
    list(
      percentage = ~ qwraps2::n_perc(drugC$outcome == 1)
    )
)


all = summary_table(data, sum)
A = summary_table(drugA, sumA)
B = summary_table(drugB, sumB)
C = summary_table(drugC, sumC)
cbind(all,A,B,C)

```


|                                                                          |data (N = 478)       |drugA (N = 180)      |drugB (N = 149)      |drugC (N = 149)      |
|:-------------------------------------------------------------------------|:--------------------|:--------------------|:--------------------|:--------------------|
|**Age**                                                                   |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                    |28.38 &plusmn; 25.33 |28.79 &plusmn; 25.77 |28.38 &plusmn; 25.12 |27.90 &plusmn; 25.17 |
|&nbsp;&nbsp; Range                                                        |1-94                 |1-94                 |1-84                 |1-85                 |
|**Gender**                                                                |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Female                                                       |207 (43.31%)         |82 (45.56%)          |60 (40.27%)          |65 (43.62%)          |
|&nbsp;&nbsp; Male                                                         |271 (56.69%)         |98 (54.44%)          |89 (59.73%)          |84 (56.38%)          |
|**Race**                                                                  |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Black                                                        |201 (42.05%)         |77 (42.78%)          |58 (38.93%)          |66 (44.30%)          |
|&nbsp;&nbsp; White                                                        |209 (43.72%)         |80 (44.44%)          |68 (45.64%)          |61 (40.94%)          |
|&nbsp;&nbsp; Asian                                                        |18 (3.77%)           |7 (3.89%)            |6 (4.03%)            |5 (3.36%)            |
|&nbsp;&nbsp; Other                                                        |14 (2.93%)           |6 (3.33%)            |3 (2.01%)            |5 (3.36%)            |
|&nbsp;&nbsp; Unknown                                                      |36 (7.53%)           |10 (5.56%)           |14 (9.40%)           |12 (8.05%)           |
|**Ethnicity**                                                             |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Hispanic                                                     |0 (NaN%)             |0 (NaN%)             |0 (NaN%)             |0 (NaN%)             |
|&nbsp;&nbsp; Non-Hispanic                                                 |0 (NaN%)             |0 (NaN%)             |0 (NaN%)             |0 (NaN%)             |
|**Weight(Kg)**                                                            |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd)                                                    |51.74 &plusmn; 31.64 |51.86 &plusmn; 31.29 |52.98 &plusmn; 33.95 |50.35 &plusmn; 29.76 |
|&nbsp;&nbsp; Range                                                        |9-157.4              |9.2-150              |9-157.4              |9.0909-128.6         |
|**History of epilepsy**                                                   |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Yes                                                          |344 (72.27%)         |128 (71.51%)         |108 (72.97%)         |108 (72.48%)         |
|&nbsp;&nbsp; No                                                           |132 (27.73%)         |51 (28.49%)          |40 (27.03%)          |41 (27.52%)          |
|&nbsp;&nbsp; NA                                                           |2(0.42%)             |1(0.56%)             |1(0.67%)             |0(0%)                |
|**Aetiology**                                                             |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Acute stroke/Hemorrhage                                      |17 (3.56%)           |6 (3.33%)            |8 (5.37%)            |3 (2.01%)            |
|&nbsp;&nbsp; Anti-epileptic drug withdrawal/non compliance                |62 (12.97%)          |25 (13.89%)          |17 (11.41%)          |20 (13.42%)          |
|&nbsp;&nbsp; CNS infection                                                |7 (1.46%)            |3 (1.67%)            |1 (0.67%)            |3 (2.01%)            |
|&nbsp;&nbsp; CNS tumor                                                    |8 (1.67%)            |2 (1.11%)            |4 (2.68%)            |2 (1.34%)            |
|&nbsp;&nbsp; Febrile illness                                              |94 (19.67%)          |33 (18.33%)          |25 (16.78%)          |36 (24.16%)          |
|&nbsp;&nbsp; Insufficient information to determine/idiopathic/cryptogenic |21 (4.39%)           |9 (5.00%)            |3 (2.01%)            |9 (6.04%)            |
|&nbsp;&nbsp; Metabolic (hypoglycemia, hyponatremia, etc.)                 |6 (1.26%)            |3 (1.67%)            |2 (1.34%)            |1 (0.67%)            |
|&nbsp;&nbsp; Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)  |30 (6.28%)           |13 (7.22%)           |9 (6.04%)            |8 (5.37%)            |
|&nbsp;&nbsp; Unprovoked                                                   |166 (34.73%)         |64 (35.56%)          |57 (38.26%)          |45 (30.20%)          |
|&nbsp;&nbsp; Other                                                        |67 (14.02%)          |22 (12.22%)          |23 (15.44%)          |22 (14.77%)          |
|**Lorazepam equivalents**                                                 |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; In mg for those weighing ≥32 kg                              |4.85 &plusmn; 2.42   |5.59 &plusmn; 2.36   |5.48 &plusmn; 2.09   |5.84 &plusmn; 2.65   |
|&nbsp;&nbsp; NA                                                           |2(0.42%)             |0(0%)                |0(0%)                |0(0%)                |
|&nbsp;&nbsp; In mg/kg for those weighing <32 kg                           |0.21 &plusmn; 0.10   |0.21 &plusmn; 0.10   |0.20 &plusmn; 0.10   |0.21 &plusmn; 0.10   |
|&nbsp;&nbsp; NA                                                           |295(0.42%)           |1(1.47%)             |1(1.59%)             |0(0%)                |
|**Success**                                                               |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; percentage                                                   |232 (48.54%)         |84 (46.67%)          |70 (46.98%)          |78 (52.35%)          |