---
title: "Data Analysis"
author: "Xiaoyang Li"
date: "2021/7/1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F,message = F, results = "hide",
                      fig.width = 16,fig.height = 8)
```


```{r data import}

library(tidyverse)
library(patchwork)
library(MASS)

data = read_csv("./data/newData.csv") %>% dplyr::select(-X1) %>% 
  mutate(age_group = factor(age_group, levels = c("child", "adult", "senior" )),
         se_group = factor(se_group, levels = c("[0,30)", "[30,60)", "[60,)" )),
         Failure = recode(success, "1" = "Success", "0" = "Failure") ) %>% 
  mutate(Failure = factor(Failure, levels = c("Success", "Failure")))

str(data)  

dataA = data %>% filter(drug == "A")
dataB = data %>% filter(drug == "B")
dataC = data %>% filter(drug == "C")
```

# Bar plot with proportion as well as odds ratio / univariate analysis

Plots below include information of 

* Number of patients
* Proportion of Patients by success or not
* Odds ratio and its 95% confidence interval with the reference group (always the first subgroup)

by treatment and subgroup.

## age group

```{r}
data_ageperc = data %>% 
  group_by(drug,age_group, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

ageP = data %>%
  ggplot(aes(x = age_group, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_ageperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   
  labs(x = "Age Group", y = "Proportion") + 
  theme(axis.title.x = element_text(size=20,face = "bold"),
        axis.text.x  = element_text(size = 18),
        axis.title.y = element_text(size=20,face = "bold"),
        axis.text.y  = element_text(size = 15) ) + 
  scale_x_discrete(breaks=c("child", "adult", "senior"),
                      labels=c("Child", "Adult", "Senior"))

ageA_glm = glm(Failure ~ age_group, dataA, family = "binomial")
summary(ageA_glm)
exp(cbind(OR = coef(ageA_glm), confint(ageA_glm)))

ageB_glm = glm(Failure ~ age_group, dataB, family = "binomial")
summary(ageB_glm)
exp(cbind(OR = coef(ageB_glm), confint(ageB_glm)))
  
ageC_glm = glm(Failure ~ age_group, dataC, family = "binomial")
summary(ageC_glm)
exp(cbind(OR = coef(ageC_glm), confint(ageC_glm)))

age_odds <- data.frame(
  label = c("1", "1.64(0.80, 3.39)", "2.91(1.20, 7.29)",
            "1","1.02(0.46, 2.25)" ,"1.37(0.53, 3.57)" , 
            "1", "1.46(0.66, 3.26)" , "2.21(0.86, 5.91)" ),
  drug   = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
  x     = c("child", "adult", "senior","child", "adult", "senior","child", "adult", "senior"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",9)
)

ageP + geom_text(
  data    = age_odds,
  mapping = aes(x = x, y = y, label = label),
  size = 5
)

```

## gender

```{r}
data_genderperc = data %>% 
  group_by(drug,gender, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

genderP = data %>%
  ggplot(aes(x = gender, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_genderperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   
  labs(x = "Gender Group", y = "Proportion") +    
  theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

genderA_glm = glm(Failure ~ gender, dataA, family = "binomial")
summary(genderA_glm)
exp(cbind(OR = coef(genderA_glm), confint(genderA_glm)))

genderB_glm = glm(Failure ~ gender, dataB, family = "binomial")
summary(genderB_glm)
exp(cbind(OR = coef(genderB_glm), confint(genderB_glm)))
  
genderC_glm = glm(Failure ~ gender, dataC, family = "binomial")
summary(genderC_glm)
exp(cbind(OR = coef(genderC_glm), confint(genderC_glm)))

gender_odds <- data.frame(
  label = c("1", "1.07(0.57, 2.03)", 
            "1","1.11(0.55, 2.26)" ,
            "1", "0.84(0.42, 1.71)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("Female", "Male","Female", "Male","Female", "Male"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

genderP + geom_text(
  data    = gender_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```

## Provoked or not

```{r}
data_provokedperc = data %>% 
  group_by(drug,provoked, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

provokedP = data %>%
  ggplot(aes(x = provoked, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_provokedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   labs(x = "Provoked", y = "Proportion") +    theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

provokedA_glm = glm(Failure ~ provoked, dataA, family = "binomial")
summary(provokedA_glm)
exp(cbind(OR = coef(provokedA_glm), confint(provokedA_glm)))

provokedB_glm = glm(Failure ~ provoked, dataB, family = "binomial")
summary(provokedB_glm)
exp(cbind(OR = coef(provokedB_glm), confint(provokedB_glm)))
  
provokedC_glm = glm(Failure ~ provoked, dataC, family = "binomial")
summary(provokedC_glm)
exp(cbind(OR = coef(provokedC_glm), confint(provokedC_glm)))

provoked_odds <- data.frame(
  label = c("1", "0.98(0.51, 1.91)", 
            "1", "0.51(0.25, 1.04)",
            "1", "1.89(0.87, 4.29)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

provokedP + geom_text(
  data    = provoked_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```


## Home antiepileptic medication

```{r}
data_homemedperc = data %>% 
  group_by(drug,homemed, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

homemedP = data %>%
  ggplot(aes(x = homemed, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_homemedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   labs(x = "Home Antiepileptic Medication", y = "Proportion") +    theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

homemedA_glm = glm(Failure ~ homemed, dataA, family = "binomial")
summary(homemedA_glm)
exp(cbind(OR = coef(homemedA_glm), confint(homemedA_glm)))

homemedB_glm = glm(Failure ~ homemed, dataB, family = "binomial")
summary(homemedB_glm)
exp(cbind(OR = coef(homemedB_glm), confint(homemedB_glm)))
  
homemedC_glm = glm(Failure ~ homemed, dataC, family = "binomial")
summary(homemedC_glm)
exp(cbind(OR = coef(homemedC_glm), confint(homemedC_glm)))

homemed_odds <- data.frame(
  label = c("1", "1.02(0.52, 2.02)", 
            "1", "1.06(0.50, 2.29)",
            "1", "0.47(0.22, 0.99)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

homemedP + geom_text(
  data    = homemed_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```

## Seizure duration 0/30/60/ (n = 392)

```{r}
data_se_groupperc = data %>% 
  filter(!is.na(se_group)) %>% 
  group_by(drug,se_group, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

se_groupP = data %>%
  filter(!is.na(se_group)) %>% 
  ggplot(aes(x = se_group, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_se_groupperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   labs(x = "Seizure Duration", y = "Proportion") +    theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

se_groupA_glm = glm(Failure ~ se_group, dataA, family = "binomial")
summary(se_groupA_glm)
exp(cbind(OR = coef(se_groupA_glm), confint(se_groupA_glm)))

se_groupB_glm = glm(Failure ~ se_group, dataB, family = "binomial")
summary(se_groupB_glm)
exp(cbind(OR = coef(se_groupB_glm), confint(se_groupB_glm)))
  
se_groupC_glm = glm(Failure ~ se_group, dataC, family = "binomial")
summary(se_groupC_glm)
exp(cbind(OR = coef(se_groupC_glm), confint(se_groupC_glm)))

se_group_odds <- data.frame(
  label = c("1", "1.15(0.37, 3.85)", "1.13(0,38, 3,60)",
            "1","6.00(1.38, 42.09)" ,"4.85(1.16, 33.17)" , 
            "1", "1.09(0.33, 3.84)", "0.96(0.31, 3.16)" ),
  drug   = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
  x     = c("[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",9)
)

se_groupP + geom_text(
  data    = se_group_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```

## Benzodiazepine prior to ED visit (n = 346)

```{r}
data_benzoperc = data %>% 
  filter(!is.na(benzo)) %>% 
  group_by(drug,benzo, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzoP = data %>% 
  filter(!is.na(benzo))%>%
  ggplot(aes(x = benzo, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_benzoperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   labs(x = "Benzodiazepine Prior to ED Visit", y = "Proportion") +    theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

benzoA_glm = glm(Failure ~ benzo, dataA, family = "binomial")
summary(benzoA_glm)
exp(cbind(OR = coef(benzoA_glm), confint(benzoA_glm)))

benzoB_glm = glm(Failure ~ benzo, dataB, family = "binomial")
summary(benzoB_glm)
exp(cbind(OR = coef(benzoB_glm), confint(benzoB_glm)))
  
benzoC_glm = glm(Failure ~ benzo, dataC, family = "binomial")
summary(benzoC_glm)
exp(cbind(OR = coef(benzoC_glm), confint(benzoC_glm)))

benzo_odds <- data.frame(
  label = c("1", "0.74(0.36, 1.50)", 
            "1", "1.08(0.50, 2.33)",
            "1", "0.92(0.43, 1.97)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

benzoP + geom_text(
  data    = benzo_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)
```


## Number of doses of benzodiazepine given prior to study drug
(3-7 doses vs 1-2 doses)

```{r}
data_benzonumperc = data %>% 
  group_by(drug,benzonum, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzonumP = data %>%
  ggplot(aes(x = benzonum, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1,
            size = 6)   +
  geom_text(data = data_benzonumperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~drug) +   labs(x = "Number of Benzodiazepine Doses", y = "Proportion") +    theme(axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

benzonumA_glm = glm(Failure ~ benzonum, dataA, family = "binomial")
summary(benzonumA_glm)
exp(cbind(OR = coef(benzonumA_glm), confint(benzonumA_glm)))

benzonumB_glm = glm(Failure ~ benzonum, dataB, family = "binomial")
summary(benzonumB_glm)
exp(cbind(OR = coef(benzonumB_glm), confint(benzonumB_glm)))
  
benzonumC_glm = glm(Failure ~ benzonum, dataC, family = "binomial")
summary(benzonumC_glm)
exp(cbind(OR = coef(benzonumC_glm), confint(benzonumC_glm)))

benzonum_odds <- data.frame(
  label = c("1", "2.48(1.31, 4.79)", 
            "1", "1.26(0.63, 2.54)",
            "1", "1.11(0.54, 2.28)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("1~2", "3~7","1~2", "3~7","1~2", "3~7"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

benzonumP + geom_text(
  data    = benzonum_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)
```


## Time of 1st dose of benzodiazepine to time of study drug administration 0/15/30/45/ (n = 337)

Delete

# Variable selection 

## include 322 patients after remove NA in age_group, gender, provoked, homemed, se_group, benzo, benzonum,time

```{r}
library(MASS)
data_vs1 = data %>% dplyr::select(Failure, drug, age_group,gender,provoked,homemed,se_group,benzo,benzonum,time) %>% drop_na()

data_vs1A = data_vs1 %>% filter(drug == "A") %>% dplyr::select(-drug)
data_vs1B = data_vs1 %>% filter(drug == "B") %>% dplyr::select(-drug)
data_vs1C = data_vs1 %>% filter(drug == "C") %>% dplyr::select(-drug)

# drugA
full1A = glm(Failure ~., data = data_vs1A, family = "binomial")
for1A = stepAIC(full1A, direction = "forward")
back1A = stepAIC(full1A, direction = "backward")
both1A = stepAIC(full1A, direction = "both")

summary(for1A) # keep all variables
summary(back1A) # formula = Failure ~ age_group + benzo + benzonum
summary(both1A) # formula = Failure ~ age_group + benzo + benzonum


# drugB
full1B = glm(Failure ~., data = data_vs1B, family = "binomial")
for1B = stepAIC(full1B, direction = "forward")
back1B = stepAIC(full1B, direction = "backward")
both1B = stepAIC(full1B, direction = "both")

summary(for1B) # keep all variables
summary(back1B) # formula = Failure ~ se_group
summary(both1B) # formula = Failure ~ se_group
# provoked is the last removed variable


# drugC
full1C = glm(Failure ~., data = data_vs1C, family = "binomial")
for1C = stepAIC(full1C, direction = "forward")
back1C = stepAIC(full1C, direction = "backward")
both1C = stepAIC(full1C, direction = "both")

summary(for1C) # keep all variables
summary(back1C) # formula = Failure ~ homemed
summary(both1C) # formula = Failure ~ homemed
# provoked is the last removed variable
```

**Summary:**


Forward selection's tend to keep all variables in all situation.

For drug A, both backward selection and stepwise regression generate formula as 

$$Failure \sim age + benzo + benzonum$$
For drug B, both backward selection and stepwise regression generate formula as 

$$Failure \sim se\ group$$
*Provoked is the last removed variable*


For drug C, both backward selection and stepwise regression generate formula as 

$$Failure \sim homemed$$
*Provoked is the last removed variable*


## include 392 patients after remove NA in age_group, gender, provoked, homemed, se_group,  benzonum

In this case, I exclude variables related to Benzodiazepine prior to ED visit and Time of 1st dose of benzodiazepine to time of study drug administration 0/15/30/45/. These 2 variable include large number of NAs. In addition, from the bar plot, univariate analysis, and above variable selection, they have none influence to Failure odds of drug B and drug C

```{r}
data_vs2 = data %>% dplyr::select(Failure, drug, age_group,gender,provoked,homemed,se_group,benzonum) %>% drop_na()

data_vs2A = data_vs2 %>% filter(drug == "A") %>% dplyr::select(-drug)
data_vs2B = data_vs2 %>% filter(drug == "B") %>% dplyr::select(-drug)
data_vs2C = data_vs2 %>% filter(drug == "C") %>% dplyr::select(-drug)

# drugA
full2A = glm(Failure ~., data = data_vs2A, family = "binomial")
for2A = stepAIC(full2A, direction = "forward")
back2A = stepAIC(full2A, direction = "backward")
both2A = stepAIC(full2A, direction = "both")

summary(for2A) # keep all variables
summary(back2A) # formula = Failure ~ provoked + se_group
summary(both2A) # formula = Failure ~ provoked + se_group

# drugB
full2B = glm(Failure ~., data = data_vs2B, family = "binomial")
for2B = stepAIC(full2B, direction = "forward")
back2B = stepAIC(full2B, direction = "backward")
both2B = stepAIC(full2B, direction = "both")

summary(for2B) # keep all variables
summary(back2B) # formula = Failure ~ provoked + se_group
summary(both2B) # formula = Failure ~ provoked + se_group


# drugC
full2C = glm(Failure ~., data = data_vs2C, family = "binomial")
for2C = stepAIC(full2C, direction = "forward")
back2C = stepAIC(full2C, direction = "backward")
both2C = stepAIC(full2C, direction = "both")

summary(for2C) # keep all variables
summary(back2C) # formula = Failure ~ homemed
summary(both2C) # formula = Failure ~ homemed
# provoked is the last removed variable

```

For drug B, both backward selection and stepwise regression generate formula as 

$$Failure \sim provoked + se\ group$$


For drug C, both backward selection and stepwise regression generate formula as 

$$Failure \sim homemed$$
*Provoked is the last removed variable*

```{r}
pred = glm(Failure ~ drug+ age_group+gender+provoked+homemed+se_group+benzonum+drug*age_group
    +drug*se_group+drug*benzonum+drug*homemed + drug*provoked, data = data_vs2, family = "binomial")
summary(pred)
```

