---
title: "Data Analysis"
author: "Xiaoyang Li"
date: "2021/7/1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(patchwork)
library(MASS)
```


```{r data import, include=FALSE}
data = read_csv("./data/newData.csv") %>% select(-X1) %>% 
  mutate(age_group = factor(age_group, levels = c("child", "adult", "senior" )),
         gender = recode(data$Male, "0" = "Female", "1" = "Male"),
         homemed = recode(data$home_seizure_med, "0" = "No", "1" = "Yes"),
         se_group = factor(se_group, levels = c("[0,30)", "[30,60)", "[60,)" )),
         benzo = recode(data$benzos_pre_ed, "0" = "No", "1" = "Yes"),
         benzonum = case_when(dose_benzo <= 2 ~ "1~2",
                              dose_benzo > 2 ~ "3~7"),
         time =  case_when(time_benzo < 15 ~ "[0,15)",
                     time_benzo >= 15 & time_benzo < 30 ~ "[15,30)",
                     time_benzo >= 30 & time_benzo < 45 ~ "[30,45)",
                     time_benzo >= 45 ~ "[45,)")) 
  
  
dataA = data %>% filter(drug == "A")
dataB = data %>% filter(drug == "B")
dataC = data %>% filter(drug == "C")
```

# bar plot with proportion as well as odds ratio / univariate analysis

Plots below include information of 

* Number of patients
* Proportion of Patients by success or not
* Odds ratio and its 95% confidence interval with the reference group (always the first subgroup)

by treatment and subgroup.

## age group

```{r}
data_ageperc = data %>% 
  group_by(drug,age_group, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

ageP = data %>%
  ggplot(aes(x = age_group, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_ageperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

ageA_glm = glm(success ~ age_group, dataA, family = "binomial")
summary(ageA_glm)
exp(cbind(OR = coef(ageA_glm), confint(ageA_glm)))

ageB_glm = glm(success ~ age_group, dataB, family = "binomial")
summary(ageB_glm)
exp(cbind(OR = coef(ageB_glm), confint(ageB_glm)))
  
ageC_glm = glm(success ~ age_group, dataC, family = "binomial")
summary(ageC_glm)
exp(cbind(OR = coef(ageC_glm), confint(ageC_glm)))

age_odds <- data.frame(
  label = c("1", "0.61(0.30, 1.25)", "0.34(0.14, 0.83)",
            "1","0.98(0.44, 2.18)" ,"0.73(0.28, 1.88)" , 
            "1", "0.68(0.31, 1.52)", "0.45(0.17, 1.17)" ),
  drug   = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
  x     = c("child", "adult", "senior","child", "adult", "senior","child", "adult", "senior"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,9)
)

ageP + geom_text(
  data    = age_odds,
  mapping = aes(x = x, y = y, label = label)
)

```

## gender

```{r}
data_genderperc = data %>% 
  group_by(drug,gender, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

genderP = data %>%
  ggplot(aes(x = gender, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_genderperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

genderA_glm = glm(success ~ gender, dataA, family = "binomial")
summary(genderA_glm)
exp(cbind(OR = coef(genderA_glm), confint(genderA_glm)))

genderB_glm = glm(success ~ gender, dataB, family = "binomial")
summary(genderB_glm)
exp(cbind(OR = coef(genderB_glm), confint(genderB_glm)))
  
genderC_glm = glm(success ~ gender, dataC, family = "binomial")
summary(genderC_glm)
exp(cbind(OR = coef(genderC_glm), confint(genderC_glm)))

gender_odds <- data.frame(
  label = c("1", "0.93(0.49, 1.77)", 
            "1","0.90(0.44, 1.81)" ,
            "1", "1.19(0.59, 2.40)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("Female", "Male","Female", "Male","Female", "Male"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,6)
  
)

genderP + geom_text(
  data    = gender_odds,
  mapping = aes(x = x, y = y, label = label)
)

```

## Provoked or not

```{r}
data_provokedperc = data %>% 
  group_by(drug,provoked, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

provokedP = data %>%
  ggplot(aes(x = provoked, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_provokedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

provokedA_glm = glm(success ~ provoked, dataA, family = "binomial")
summary(provokedA_glm)
exp(cbind(OR = coef(provokedA_glm), confint(provokedA_glm)))

provokedB_glm = glm(success ~ provoked, dataB, family = "binomial")
summary(provokedB_glm)
exp(cbind(OR = coef(provokedB_glm), confint(provokedB_glm)))
  
provokedC_glm = glm(success ~ provoked, dataC, family = "binomial")
summary(provokedC_glm)
exp(cbind(OR = coef(provokedC_glm), confint(provokedC_glm)))

provoked_odds <- data.frame(
  label = c("1", "1.02(0.52, 1.98)", 
            "1", "1.95(0.96, 4.02)",
            "1", "0.53(0.23, 1.15)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,6)
  
)

provokedP + geom_text(
  data    = provoked_odds,
  mapping = aes(x = x, y = y, label = label)
)

```


## Home antiepileptic medication

```{r}
data_homemedperc = data %>% 
  group_by(drug,homemed, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

homemedP = data %>%
  ggplot(aes(x = homemed, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_homemedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

homemedA_glm = glm(success ~ homemed, dataA, family = "binomial")
summary(homemedA_glm)
exp(cbind(OR = coef(homemedA_glm), confint(homemedA_glm)))

homemedB_glm = glm(success ~ homemed, dataB, family = "binomial")
summary(homemedB_glm)
exp(cbind(OR = coef(homemedB_glm), confint(homemedB_glm)))
  
homemedC_glm = glm(success ~ homemed, dataC, family = "binomial")
summary(homemedC_glm)
exp(cbind(OR = coef(homemedC_glm), confint(homemedC_glm)))

homemed_odds <- data.frame(
  label = c("1", "0.98(0.49, 1.92)", 
            "1", "0.94(0.44, 2.01)",
            "1", "2.11(1.01, 4.48)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,6)
  
)

homemedP + geom_text(
  data    = homemed_odds,
  mapping = aes(x = x, y = y, label = label)
)

```

## Seizure duration 0/30/60/ (n = 392)

```{r}
data_se_groupperc = data %>% 
  filter(!is.na(se_group)) %>% 
  group_by(drug,se_group, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

se_groupP = data %>%
  filter(!is.na(se_group)) %>% 
  ggplot(aes(x = se_group, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_se_groupperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

se_groupA_glm = glm(success ~ se_group, dataA, family = "binomial")
summary(se_groupA_glm)
exp(cbind(OR = coef(se_groupA_glm), confint(se_groupA_glm)))

se_groupB_glm = glm(success ~ se_group, dataB, family = "binomial")
summary(se_groupB_glm)
exp(cbind(OR = coef(se_groupB_glm), confint(se_groupB_glm)))
  
se_groupC_glm = glm(success ~ se_group, dataC, family = "binomial")
summary(se_groupC_glm)
exp(cbind(OR = coef(se_groupC_glm), confint(se_groupC_glm)))

se_group_odds <- data.frame(
  label = c("1", "0.87(0.26, 2.74)", "0.88(0.28, 2.61)",
            "1","0.17(0.02, 0.72)" ,"0.21(0.03, 0.86)" , 
            "1", "0.92(0.26, 3.07)", "1.03(0.32, 3.21)" ),
  drug   = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
  x     = c("[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,9)
)

se_groupP + geom_text(
  data    = se_group_odds,
  mapping = aes(x = x, y = y, label = label)
)

```

## Benzodiazepine prior to ED visit (n = 346)

```{r}
data_benzoperc = data %>% 
  filter(!is.na(benzo)) %>% 
  group_by(drug,benzo, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzoP = data %>% 
  filter(!is.na(benzo))%>%
  ggplot(aes(x = benzo, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_benzoperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

benzoA_glm = glm(success ~ benzo, dataA, family = "binomial")
summary(benzoA_glm)
exp(cbind(OR = coef(benzoA_glm), confint(benzoA_glm)))

benzoB_glm = glm(success ~ benzo, dataB, family = "binomial")
summary(benzoB_glm)
exp(cbind(OR = coef(benzoB_glm), confint(benzoB_glm)))
  
benzoC_glm = glm(success ~ benzo, dataC, family = "binomial")
summary(benzoC_glm)
exp(cbind(OR = coef(benzoC_glm), confint(benzoC_glm)))

benzo_odds <- data.frame(
  label = c("1", "1.35(0.67, 2.75)", 
            "1", "0.93(0.43, 2.00)",
            "1", "1.09(0.51, 2.35)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,6)
  
)

benzoP + geom_text(
  data    = benzo_odds,
  mapping = aes(x = x, y = y, label = label)
)
```


## Number of doses of benzodiazepine given prior to study drug
(3-7 doses vs 1-2 doses)

```{r}
data_benzonumperc = data %>% 
  group_by(drug,benzonum, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzonumP = data %>%
  ggplot(aes(x = benzonum, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_benzonumperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

benzonumA_glm = glm(success ~ benzonum, dataA, family = "binomial")
summary(benzonumA_glm)
exp(cbind(OR = coef(benzonumA_glm), confint(benzonumA_glm)))

benzonumB_glm = glm(success ~ benzonum, dataB, family = "binomial")
summary(benzonumB_glm)
exp(cbind(OR = coef(benzonumB_glm), confint(benzonumB_glm)))
  
benzonumC_glm = glm(success ~ benzonum, dataC, family = "binomial")
summary(benzonumC_glm)
exp(cbind(OR = coef(benzonumC_glm), confint(benzonumC_glm)))

benzonum_odds <- data.frame(
  label = c("1", "0.40(0.21, 0.76)", 
            "1", "0.79(0.39, 1.58)",
            "1", "0.90(0.43, 1.85)"),
  drug   = c("A", "A",  "B", "B", "C", "C"),
  x     = c("1~2", "3~7","1~2", "3~7","1~2", "3~7"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,6)
  
)

benzonumP + geom_text(
  data    = benzonum_odds,
  mapping = aes(x = x, y = y, label = label)
)
```


## Time of 1st dose of benzodiazepine to time of study drug administration 0/15/30/45/ (n = 337)

```{r}
data_timeperc = data %>% 
  filter(!is.na(time)) %>% 
  group_by(drug,time, success) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

timeP = data %>%
  filter(!is.na(time)) %>% 
  ggplot(aes(x = time, fill = factor(success))) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1)   +
  geom_text(data = data_timeperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 2, 
            position = position_fill()) +
  facet_grid(.~drug)

timeA_glm = glm(success ~ time, dataA, family = "binomial")
summary(timeA_glm)
exp(cbind(OR = coef(timeA_glm), confint(timeA_glm)))

timeB_glm = glm(success ~ time, dataB, family = "binomial")
summary(timeB_glm)
exp(cbind(OR = coef(timeB_glm), confint(timeB_glm)))
  
timeC_glm = glm(success ~ time, dataC, family = "binomial")
summary(timeC_glm)
exp(cbind(OR = coef(timeC_glm), confint(timeC_glm)))

time_odds <- data.frame(
  label = c("1", "1.45(0.44, 4,61)", "0.60(0.18, 1.89)", "1.04(0.34, 3.06)",
            "1", "3.2(0.89, 12.5)" ,"1.22(0.33, 4.88)" , "1.96(0.57, 7.31)",
            "1", "0.82(0.27, 2.41)", "1.02(0.45, 3.47)", "1.40(0.45, 4.29)"),
  drug   = c("A", "A", "A", "A", "B", "B", "B","B", "C", "C", "C", "C"),
  x     = c("[0,15)", "[15,30)", "[30,45)","[45,)", "[0,15)", "[15,30)", "[30,45)","[45,)","[0,15)", "[15,30)", "[30,45)","[45,)"),
  y     = c(1.03, 1.03, 1.03,1.03, 1.03, 1.03,1.03, 1.03, 1.03,1.03, 1.03, 1.03),
  success = rep(1,12)
)

timeP + geom_text(
  data    = time_odds,
  mapping = aes(x = x, y = y, label = label)
)

```



# variable selection 

## include 322 patients after remove NA in age_group, gender, provoked, homemed, se_group, benzo, benzonum,time

```{r}
library(MASS)
data_vs1 = data %>% dplyr::select(success, drug, age_group,gender,provoked,homemed,se_group,benzo,benzonum,time) %>% drop_na()

data_vs1A = data_vs1 %>% filter(drug == "A") %>% dplyr::select(-drug)
data_vs1B = data_vs1 %>% filter(drug == "B") %>% dplyr::select(-drug)
data_vs1C = data_vs1 %>% filter(drug == "C") %>% dplyr::select(-drug)

# drugA
full1A = glm(success ~., data = data_vs1A, family = "binomial")
for1A = stepAIC(full1A, direction = "forward")
back1A = stepAIC(full1A, direction = "backward")
both1A = stepAIC(full1A, direction = "both")

summary(for1A) # keep all variables
summary(back1A) # formula = success ~ age_group + benzo + benzonum
summary(both1A) # formula = success ~ age_group + benzo + benzonum


# drugB
full1B = glm(success ~., data = data_vs1B, family = "binomial")
for1B = stepAIC(full1B, direction = "forward")
back1B = stepAIC(full1B, direction = "backward")
both1B = stepAIC(full1B, direction = "both")

summary(for1B) # keep all variables
summary(back1B) # formula = success ~ se_group
summary(both1B) # formula = success ~ se_group
# provoked is the last removed variable


# drugC
full1C = glm(success ~., data = data_vs1C, family = "binomial")
for1C = stepAIC(full1C, direction = "forward")
back1C = stepAIC(full1C, direction = "backward")
both1C = stepAIC(full1C, direction = "both")

summary(for1C) # keep all variables
summary(back1C) # formula = success ~ homemed
summary(both1C) # formula = success ~ homemed
# provoked is the last removed variable
```

Summary: 

Forward selection's tend to keep all variables in all situation.

For drug A, both backward selection and stepwise regression generate formula as 

$$success \sim age + benzo + benzonum$$
For drug B, both backward selection and stepwise regression generate formula as 

$$success \sim se\ group$$
*Provoked is the last removed variable*


For drug C, both backward selection and stepwise regression generate formula as 

$$success \sim homemed$$
*Provoked is the last removed variable*


## include 392 patients after remove NA in age_group, gender, provoked, homemed, se_group,  benzonum

In this case, I exclude variables related to Benzodiazepine prior to ED visit and Time of 1st dose of benzodiazepine to time of study drug administration 0/15/30/45/. These 2 variable include large number of NAs. In addition, from the bar plot, univariate analysis, and above variable selection, they have none influence to success odds of drug B and drug C

```{r}
data_vs2 = data %>% dplyr::select(success, drug, age_group,gender,provoked,homemed,se_group,benzonum) %>% drop_na()

data_vs2B = data_vs2 %>% filter(drug == "B") %>% dplyr::select(-drug)
data_vs2C = data_vs2 %>% filter(drug == "C") %>% dplyr::select(-drug)

# drugB
full2B = glm(success ~., data = data_vs2B, family = "binomial")
for2B = stepAIC(full2B, direction = "forward")
back2B = stepAIC(full2B, direction = "backward")
both2B = stepAIC(full2B, direction = "both")

summary(for2B) # keep all variables
summary(back2B) # formula = success ~ provoked + se_group
summary(both2B) # formula = success ~ provoked + se_group


# drugC
full2C = glm(success ~., data = data_vs2C, family = "binomial")
for2C = stepAIC(full2C, direction = "forward")
back2C = stepAIC(full2C, direction = "backward")
both2C = stepAIC(full2C, direction = "both")

summary(for2C) # keep all variables
summary(back2C) # formula = success ~ homemed
summary(both2C) # formula = success ~ homemed
# provoked is the last removed variable

```

For drug B, both backward selection and stepwise regression generate formula as 

$$success \sim provoked + se\ group$$


For drug C, both backward selection and stepwise regression generate formula as 

$$success \sim homemed$$
*Provoked is the last removed variable*
