---
title: "Multivariate"
author: "Xiaoyang Li"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(patchwork)
library(MASS)

data = read_csv("./data/newData.csv") %>% dplyr::select(-X1) %>% 
  mutate(age_group = factor(age_group, levels = c("child", "adult", "senior" )),
         se_group = factor(se_group, levels = c("[0,30)", "[30,60)", "[60,)" )),
         Failure = recode(success, "1" = "Success", "0" = "Failure") ) %>% 
  mutate(Failure = factor(Failure, levels = c("Success", "Failure")))
data_vs2 = data %>% dplyr::select(Failure, drug, age_group,gender,provoked,homemed,se_group,benzonum, idmatchA) %>% drop_na()


data_vs2A = data_vs2 %>% filter(drug == "A") %>% dplyr::select(-drug)
data_vs2B = data_vs2 %>% filter(drug == "B") %>% dplyr::select(-drug)
data_vs2C = data_vs2 %>% filter(drug == "C") %>% dplyr::select(-drug)

```


## Variable selection 

### include 392 patients after remove NA in age_group, gender, provoked, homemed, se_group,  benzonum

In this case, I exclude variables related to Benzodiazepine prior to ED visit and Time of 1st dose of benzodiazepine to time of study drug administration 0/15/30/45/. These 2 variable include large number of NAs. In addition, from the bar plot, univariate analysis, and above variable selection, they have none influence to Failure odds of drug B and drug C


After adjusting the forward selection threshold, all of three variable selection method generate the same results


For drug A, they generate formula as 

$$Failure \sim age +benzonum$$

```{r}
glmA = glm(Failure ~age_group + benzonum, data = data_vs2A, family = "binomial")
```


For drug B, they generate formula as 

$$Failure \sim provoked + se\ group$$

```{r}
glmB = glm(Failure ~provoked + se_group, data = data_vs2B, family = "binomial") 
```

For drug C, they generate formula as 

$$Failure \sim homemed$$
*Provoked is the last removed variable*

```{r}
glmC = glm(Failure ~homemed, data = data_vs2C, family = "binomial")
```

```{r}
beta = summary(glmC)$coefficient[,1]
stderror = summary(glmC)$coefficient[,2]
OR = rbind(exp(beta), exp(beta - 1.959964 * stderror ),exp(beta + 1.959964*stderror))
OR
```

