---
title: "Supplement"
author: "Xiaoyang Li"
date: "2/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F,message = F, results = "hide",
                      fig.width = 16,fig.height = 8)

library(tidyverse)
library(patchwork)
library(MASS)

data = read_csv("./data/newData.csv") %>% dplyr::select(-X1) %>% 
  mutate(age_group = factor(age_group, levels = c("child", "adult", "senior" )),
         se_group = factor(se_group, levels = c("[0,30)", "[30,60)", "[60,)" )),
         Failure = recode(success, "1" = "Success", "0" = "Failure"),
         Drug = recode(drug, "A" = "LEV", "B" = "FOS", "C" ="VPA" ) ) %>% 
  mutate(Failure = factor(Failure, levels = c("Failure", "Success")),
         Drug = factor(Drug, levels = c("LEV", "FOS","VPA"))) 

str(data)  

dataA = data %>% filter(drug == "A")
dataB = data %>% filter(drug == "B")
dataC = data %>% filter(drug == "C")
```

# New Table 3


|                                                                 |A (N = 159)  |B (N = 131)  |C (N = 131)  |
|:----------------------------------------------------------------|:------------|:------------|:------------|
|**Stroke**                                                       |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |3 (1.89%)    |4 (3.05%)    |1 (0.76%)    |
|&nbsp;&nbsp; Failure                                             |3 (1.89%)    |4 (3.05%)    |2 (1.53%)    |
|**Electrolyte anomalies**                                        |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |2 (1.26%)    |0 (0.00%)    |0 (0.00%)    |
|&nbsp;&nbsp; Failure                                             |1 (0.63%)    |2 (1.53%)    |1 (0.76%)    |
|**CNS Tumors/CNS infection**                                     |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |1 (0.63%)    |3 (2.29%)    |0 (0.00%)    |
|&nbsp;&nbsp; Failure                                             |4 (2.52%)    |2 (1.53%)    |5 (3.82%)    |
|**Unprovoked**                                                   |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |32 (20.13%)  |22 (16.79%)  |27 (20.61%)  |
|&nbsp;&nbsp; Failure                                             |23 (14.47%)  |28 (21.37%)  |12 (9.16%)   |
|**Anti-epileptic drug withdrawal/non compliance**                |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |14 (8.81%)   |10 (7.63%)   |13 (9.92%)   |
|&nbsp;&nbsp; Failure                                             |10 (6.29%)   |5 (3.82%)    |3 (2.29%)    |
|**Febrile illness**                                              |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |22 (13.84%)  |16 (12.21%)  |20 (15.27%)  |
|&nbsp;&nbsp; Failure                                             |9 (5.66%)    |8 (6.11%)    |15 (11.45%)  |
|**Insufficient information to determine/idiopathic/cryptogenic** |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |0 (0.00%)    |2 (1.53%)    |4 (3.05%)    |
|&nbsp;&nbsp; Failure                                             |7 (4.40%)    |1 (0.76%)    |4 (3.05%)    |
|**Toxic (alcohol / drug withdrawal-not AEDs, poisoning, etc.)**  |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |6 (3.77%)    |3 (2.29%)    |3 (2.29%)    |
|&nbsp;&nbsp; Failure                                             |5 (3.14%)    |3 (2.29%)    |5 (3.82%)    |
|**Other**                                                        |&nbsp;&nbsp; |&nbsp;&nbsp; |&nbsp;&nbsp; |
|&nbsp;&nbsp; Success                                             |13 (8.18%)   |11 (8.40%)   |9 (6.87%)    |
|&nbsp;&nbsp; Failure                                             |4 (2.52%)    |7 (5.34%)    |7 (5.34%)    |

# Edited Bar plot


## age group

```{r}
data_ageperc = data %>% 
  group_by(Drug,age_group, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

ageP = data %>%
  ggplot(aes(x = age_group, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_ageperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) + 
  labs(x = "Age Group", y = "Proportion") + 
  theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),
        axis.title.x = element_text(size=20,face = "bold"),
        axis.text.x  = element_text(size = 18),
        axis.title.y = element_text(size=20,face = "bold"),
        axis.text.y  = element_text(size = 15) ) + 
  scale_x_discrete(breaks=c("child", "adult", "senior"),
                      labels=c("Child", "Adult", "Senior"))

ageA_glm = glm(Failure ~ age_group, dataA, family = "binomial")
summary(ageA_glm)
exp(cbind(OR = coef(ageA_glm), confint(ageA_glm)))

ageB_glm = glm(Failure ~ age_group, dataB, family = "binomial")
summary(ageB_glm)
exp(cbind(OR = coef(ageB_glm), confint(ageB_glm)))
  
ageC_glm = glm(Failure ~ age_group, dataC, family = "binomial")
summary(ageC_glm)
exp(cbind(OR = coef(ageC_glm), confint(ageC_glm)))

age_odds <- data.frame(
  label = c("OR(95%CI)  1          ", "1.64(0.80, 3.39)", "2.91(1.20, 7.29)",
            "1","1.02(0.46, 2.25)" ,"1.37(0.53, 3.57)" , 
            "1", "1.46(0.66, 3.26)" , "2.21(0.86, 5.91)" ),
  Drug   = factor(c("LEV", "LEV", "LEV", "FOS", "FOS","FOS", "VPA", "VPA", "VPA"), levels = c("LEV", "FOS","VPA")),
  x     = c("child", "adult", "senior","child", "adult", "senior","child", "adult", "senior"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",9)
)


ageP + geom_text(
  data    = age_odds,
  mapping = aes(x = x, y = y, label = label),
  size = 5
)

```

## Provoked or not

```{r}
data_provokedperc = data %>% 
  group_by(Drug,provoked, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

provokedP = data %>%
  ggplot(aes(x = provoked, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_provokedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) +   labs(x = "Provoked", y = "Proportion") +    theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

provokedA_glm = glm(Failure ~ provoked, dataA, family = "binomial")
summary(provokedA_glm)
exp(cbind(OR = coef(provokedA_glm), confint(provokedA_glm)))

provokedB_glm = glm(Failure ~ provoked, dataB, family = "binomial")
summary(provokedB_glm)
exp(cbind(OR = coef(provokedB_glm), confint(provokedB_glm)))
  
provokedC_glm = glm(Failure ~ provoked, dataC, family = "binomial")
summary(provokedC_glm)
exp(cbind(OR = coef(provokedC_glm), confint(provokedC_glm)))

provoked_odds <- data.frame(
  label = c("OR(95%CI)  1                      ", "0.98(0.51, 1.91)", 
            "1", "0.51(0.25, 1.04)",
            "1", "1.89(0.87, 4.29)"),
  Drug   = factor(c("LEV", "LEV",  "FOS", "FOS", "VPA", "VPA"),levels = c("LEV", "FOS","VPA")),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

provokedP + geom_text(
  data    = provoked_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```


## Home antiepileptic medication

```{r}
data_homemedperc = data %>% 
  group_by(Drug,homemed, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

homemedP = data %>%
  ggplot(aes(x = homemed, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_homemedperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) +   labs(x = "Home Antiepileptic Medication", y = "Proportion") +    theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

homemedA_glm = glm(Failure ~ homemed, dataA, family = "binomial")
summary(homemedA_glm)
exp(cbind(OR = coef(homemedA_glm), confint(homemedA_glm)))

homemedB_glm = glm(Failure ~ homemed, dataB, family = "binomial")
summary(homemedB_glm)
exp(cbind(OR = coef(homemedB_glm), confint(homemedB_glm)))
  
homemedC_glm = glm(Failure ~ homemed, dataC, family = "binomial")
summary(homemedC_glm)
exp(cbind(OR = coef(homemedC_glm), confint(homemedC_glm)))

homemed_odds <- data.frame(
  label = c("OR(95%CI)  1                      ", "1.02(0.52, 2.02)", 
            "1", "1.06(0.50, 2.29)",
            "1", "0.47(0.22, 0.99)"),
  Drug   = factor(c("LEV", "LEV",  "FOS", "FOS", "VPA", "VPA"),levels = c("LEV", "FOS","VPA")),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

homemedP + geom_text(
  data    = homemed_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```


## Seizure duration 0/30/60/ (n = 392)

```{r}
data_se_groupperc = data %>% 
  filter(!is.na(se_group)) %>% 
  group_by(Drug,se_group, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

se_groupP = data %>%
  filter(!is.na(se_group)) %>% 
  ggplot(aes(x = se_group, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_se_groupperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) +   labs(x = "Seizure Duration", y = "Proportion") +    theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

se_groupA_glm = glm(Failure ~ se_group, dataA, family = "binomial")
summary(se_groupA_glm)
exp(cbind(OR = coef(se_groupA_glm), confint(se_groupA_glm)))

se_groupB_glm = glm(Failure ~ se_group, dataB, family = "binomial")
summary(se_groupB_glm)
exp(cbind(OR = coef(se_groupB_glm), confint(se_groupB_glm)))
  
se_groupC_glm = glm(Failure ~ se_group, dataC, family = "binomial")
summary(se_groupC_glm)
exp(cbind(OR = coef(se_groupC_glm), confint(se_groupC_glm)))

se_group_odds <- data.frame(
  label = c("OR(95%CI)  1         ", "1.15(0.37, 3.85)", "1.13(0,38, 3,60)",
            "1","6.00(1.38, 42.09)" ,"4.85(1.16, 33.17)" , 
            "1", "1.09(0.33, 3.84)", "0.96(0.31, 3.16)" ),
  Drug   = factor(c("LEV", "LEV", "LEV", "FOS", "FOS","FOS", "VPA", "VPA", "VPA"),levels = c("LEV", "FOS","VPA")),
  x     = c("[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)","[0,30)", "[30,60)", "[60,)"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",9)
)

se_groupP + geom_text(
  data    = se_group_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)

```

## Benzodiazepine prior to ED visit (n = 346)

```{r}
data_benzoperc = data %>% 
  filter(!is.na(benzo)) %>% 
  group_by(Drug,benzo, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzoP = data %>% 
  filter(!is.na(benzo))%>%
  ggplot(aes(x = benzo, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_benzoperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) +   labs(x = "Benzodiazepine Prior to ED Visit", y = "Proportion") +    theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

benzoA_glm = glm(Failure ~ benzo, dataA, family = "binomial")
summary(benzoA_glm)
exp(cbind(OR = coef(benzoA_glm), confint(benzoA_glm)))

benzoB_glm = glm(Failure ~ benzo, dataB, family = "binomial")
summary(benzoB_glm)
exp(cbind(OR = coef(benzoB_glm), confint(benzoB_glm)))
  
benzoC_glm = glm(Failure ~ benzo, dataC, family = "binomial")
summary(benzoC_glm)
exp(cbind(OR = coef(benzoC_glm), confint(benzoC_glm)))

benzo_odds <- data.frame(
  label = c("OR(95%CI)  1                      ", "0.74(0.36, 1.50)", 
            "1", "1.08(0.50, 2.33)",
            "1", "0.92(0.43, 1.97)"),
  Drug   = factor(c("LEV", "LEV",  "FOS", "FOS", "VPA", "VPA"),levels = c("LEV", "FOS","VPA")),
  x     = c("No", "Yes","No", "Yes","No", "Yes"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

benzoP + geom_text(
  data    = benzo_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)
```


## Number of doses of benzodiazepine given prior to study drug
(3-7 doses vs 1-2 doses)

```{r}
data_benzonumperc = data %>% 
  group_by(Drug,benzonum, Failure) %>% 
  summarise(n = n() ) %>% 
  mutate(pct = round(n / sum(n), 3)) 

benzonumP = data %>%
  ggplot(aes(x = benzonum, fill = Failure)) +
  geom_bar(stat = "count",position="fill")+
  geom_text(stat = "count", 
            aes(label = after_stat(count)),
            position="fill", 
            vjust = 1.5,
            size = 6)   +
  geom_text(data = data_benzonumperc, stat = "identity", 
            aes(label = paste0(pct*100, "%"), y = pct),
            vjust = 3, 
            position = position_fill(),
            size = 6) +
  facet_grid(.~Drug) +   labs(x = "Number of Benzodiazepine Doses", y = "Proportion") +    theme(legend.text = element_text(size=20), legend.title = element_blank(),legend.position="top",strip.text.x = element_text(size = 15),axis.title.x = element_text(size=20,face = "bold"),         axis.text.x  = element_text(size = 18),         axis.title.y = element_text(size=20,face = "bold"),         axis.text.y  = element_text(size = 15) )

benzonumA_glm = glm(Failure ~ benzonum, dataA, family = "binomial")
summary(benzonumA_glm)
exp(cbind(OR = coef(benzonumA_glm), confint(benzonumA_glm)))

benzonumB_glm = glm(Failure ~ benzonum, dataB, family = "binomial")
summary(benzonumB_glm)
exp(cbind(OR = coef(benzonumB_glm), confint(benzonumB_glm)))
  
benzonumC_glm = glm(Failure ~ benzonum, dataC, family = "binomial")
summary(benzonumC_glm)
exp(cbind(OR = coef(benzonumC_glm), confint(benzonumC_glm)))

benzonum_odds <- data.frame(
  label = c("OR(95%CI)  1                      ", "2.48(1.31, 4.79)", 
            "1", "1.26(0.63, 2.54)",
            "1", "1.11(0.54, 2.28)"),
  Drug   = factor(c("LEV", "LEV",  "FOS", "FOS", "VPA", "VPA"),levels = c("LEV", "FOS","VPA")),
  x     = c("1~2", "3~7","1~2", "3~7","1~2", "3~7"),
  y     = c(-0.03, -0.03, -0.03,-0.03, -0.03, -0.03),
  Failure = rep("Failure",6)
  
)

benzonumP + geom_text(
  data    = benzonum_odds,
  mapping = aes(x = x, y = y, label = label),
            size = 5
)
```


